A meta-analysis of mental rotation ability in the first years of life

### 2022-04-27 code/analysis.Rmd
Draw HPDI as outlines in regression plot

@@

# Regression plot
dat_reg %>%
  ggplot(aes(x = age * 12, y = gi)) +
  geom_hline(yintercept = 0, linetype = "dashed") +

  # Regression lines and HPDIs - Habituation tasks
  stat_lineribbon(
    aes(y = .epred, color = gender_task),
    data = draws_reg,
    alpha = .4,
    point_interval = "mean_hdi"
  ) +
  # Individual study effect sizes - Habituation tasks
  geom_point(aes(color = gender_task, size = ni), shape = 0) +
  scale_color_manual(
    values = habi_colors,
    breaks = names(habi_colors),
    labels = c("Females", "Males", "Mixed gender"),
    na.value = NA
  ) +
  guides(color = guide_legend(
    title = "Habituation tasks",
    override.aes = list(fill = NA),
    order = 1
  )) +

  # Regression lines and HPDIs - VoE tasks
  ggnewscale::new_scale_color() +
  stat_lineribbon(
    aes(y = .epred, color = gender_task),
    data = draws_reg,
    alpha = .4,
    fill = NA,
    point_interval = "mean_hdi"
  ) +
  # Individual study effect sizes - VoE tasks
  geom_point(aes(color = gender_task, size = ni), shape = 0) +
  scale_color_manual(
    values = voe_colors,
    breaks = names(voe_colors),
    labels = c("Mixed gender"),
    na.value = NA
  ) +
  guides(
    color = guide_legend(
      title = "Violation of\nexpectation tasks"
    ),
    order = 2
  ) +

  # Styling
  coord_cartesian(expand = FALSE) +
  scale_x_continuous(limits = c(2.9, 16.1), breaks = seq(3, 16, 1)) +
  scale_y_continuous(limits = c(-1.2, 2.2), breaks = seq(-1, 2, 0.5)) +
  scale_fill_grey(
    start = 0.9, end = 0.7,
    labels = as_mapper(~ scales::percent(as.numeric(.x)))
  ) +
  labs(
    x = "Age (months)",
    y = expression("Hedges'" ~ italic("g")),
    fill = "Bayesian HPDI",
    size = "Sample size"
  ) +
  theme_bw() +
  theme(
    legend.key = element_blank(),
    panel.border = element_rect(size = 1),
    panel.grid = element_blank(), # element_line(color = "grey90"),
    text = element_text(family = "Helvetica"),
  )

>>>>

# Summarise to obtain HPDIs
draws_reg_hdi <- mean_hdi(draws_reg)

@@

# Regression plot
dat_reg %>%
  ggplot(aes(x = age * 12, y = gi)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  # Regression lines - Habituation tasks
  geom_lineribbon(
    aes(y = .epred, ymin = .lower, ymax = .upper, color = gender_task),
    data = draws_reg_hdi,
    fill = NA
  ) +
  # Bayesian HPDIs - Habituation tasks
  geom_ribbon(
    aes(ymin = .lower, ymax = .upper, color = gender_task),
    data = draws_reg_hdi,
    fill = NA
  ) +
  # Individual study effect sizes - Habituation tasks
  geom_point(aes(color = gender_task, size = ni), shape = 0) +
  scale_color_manual(
    values = habi_colors,
    breaks = names(habi_colors),
    labels = c("Females", "Males", "Mixed gender"),
    na.value = NA
  ) +
  guides(color = guide_legend(
    title = "Habituation tasks",
    override.aes = list(fill = NA),
    order = 1
  )) +
  ggnewscale::new_scale_color() +
  # Regression lines - VoE tasks
  geom_lineribbon(
    aes(y = .epred, ymin = .lower, ymax = .upper, color = gender_task),
    data = draws_reg_hdi,
    fill = NA
  ) +
  # Bayesian HPDIs - VoE tasks
  geom_ribbon(
    aes(ymin = .lower, ymax = .upper, color = gender_task),
    data = draws_reg_hdi,
    fill = NA
  ) +
  # Individual study effect sizes - VoE tasks
  geom_point(aes(color = gender_task, size = ni), shape = 0) +
  scale_color_manual(
    values = voe_colors,
    breaks = names(voe_colors),
    labels = c("Mixed gender"),
    na.value = NA
  ) +
  guides(
    color = guide_legend(
      title = "Violation of\nexpectation tasks"
    ),
    order = 2
  ) +
  # Styling
  coord_cartesian(expand = FALSE) +
  scale_x_continuous(limits = c(2.9, 16.1), breaks = seq(3, 16, 1)) +
  scale_y_continuous(limits = c(-1.2, 2.2), breaks = seq(-1, 2, 0.5)) +
  labs(
    x = "Age (months)",
    y = expression("Hedges'" ~ italic("g")),
    fill = "Bayesian HPDI",
    size = "Sample size"
  ) +
  theme_bw() +
  theme(
    legend.key = element_blank(),
    panel.border = element_rect(size = 1),
    panel.grid = element_blank(), # element_line(color = "grey90"),
    text = element_text(family = "Helvetica"),
  )
